\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}
\usepackage{paracol}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex{}
  % If using xelatex or lualatex:
  \setmainfont{Lato}
\else
  % If using pdflatex:
  \usepackage[default]{lato}
\fi

\definecolor{NiceBlue}{HTML}{0472c3}
\definecolor{SlateGrey}{HTML}{202020}
\definecolor{LightGrey}{HTML}{333333}
\colorlet{tagline}{NiceBlue}
\colorlet{heading}{NiceBlue}
\colorlet{headingrule}{NiceBlue}
\colorlet{subheading}{NiceBlue}
\colorlet{accent}{NiceBlue}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% My additional commands. %%
\NewInfoField{githubinfo}{\faGithub}[https://]
\newcommand{\myGithubUsername}{MatejaMaric}
\newcommand{\cvproject}[3]{
  {\large\color{emphasis}#1\par}
  \smallskip\normalsize
  \ifstrequal{#2}{}{}{{\small\makebox[0.5\linewidth][l]{\faGlobe~\href{https://#2}{#2}}}}
  \ifstrequal{#3}{}{}{{\small\makebox[0.5\linewidth][l]{\faGithub~\href{https://github.com/\myGithubUsername/#3}{#3}}}}\par
  \medskip\normalsize
}
\renewcommand{\divider}{\textcolor{body!60}{\hdashrule{\linewidth}{0.6pt}{0.5ex}}\medskip}
\renewcommand{\cvtag}[1]{
  \tikz[baseline]\node[anchor=base,draw=body!60,rounded corners,inner xsep=1ex,inner ysep =0.75ex,text height=1.5ex,text depth=.25ex,line width=0.6pt]{#1};
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\name{Mateja Mari\'c}
\tagline{Back End Engineer}
\personalinfo{
  \location{Belgrade, Serbia}
  \homepage{matejamaric.com}
  \email{mail@matejamaric.com}
  \githubinfo{github.com/\myGithubUsername}
  \linkedin{mateja-m-maric}
  %\phone{+000 00 000 0000}
}

\makecvheader{}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\cvsection{Work Experience}

\cvevent{Back End Developer}{Holycode (eJobs team)}{July 2023 --- Present}{Belgrade, Serbia}

\begin{itemize}
\item Holycode is a nearshoring software development company in which I work as a Back End Developer in eJobs team.
\item eJobs Group is the first platform for online job posting in Romania, founded in 1999, and the leader in that market.
\item I'm currently working on a new product that allows people to apply for a job without a CV.
\item The system is made using Event Sourced Architecture. Technologies that I use daily are Go, EventStoreDB and Postgres.
\end{itemize}

\medskip

\cvevent{Full Stack Engineer}{Holycode (C Wire team)}{April 2022 --- July 2023}{Belgrade, Serbia}

\begin{itemize}
\item Holycode is a nearshoring software development company in which I worked as a Full Stack Engineer in C Wire team.
\item C Wire is a Swiss AdTech startup providing it’s in-house cookie-free contextual advertising solution.
\item I expanded the ad serving capability of the system by adding OpenRTB support.
      I was improving the system that collects and processes user-interaction events generated by the ads we served.
\item Technologies that I used were Go, TypeScript, Kubernetes, Docker, Apache Kafka, Clickhouse, PostgreSQL, Redis and AWS.
\end{itemize}

\medskip

\cvevent{JavaScript Developer}{Computer Rock}{September 2021 --- April 2022}{Belgrade, Serbia}

\begin{itemize}
\item Computer Rock is a Swiss offshoring software development company with additional offices in UK, Germany and Serbia.
\item I worked on the frontend implementation of a Chinese corporate clients
      new website. I worked directly with the product manager and senior management
      team to define and groom tickets and implementation, advising as required
      on approach and implementation. I also worked on the Web UI of a British
      client's real estate data extraction and analysis tool.
\item Technologies that I used daily were JavaScript, Vue.js, Nuxt.js and SCSS.
\end{itemize}



\cvsection{Technologies}

\cvsubsection{Languages: }
\cvtag{Go}
\cvtag{TypeScript}
\cvtag{SQL}

\smallskip
\cvsubsection{Databases: }
\cvtag{EventStoreDB}
\cvtag{PostgreSQL}
\cvtag{Clickhouse}
\cvtag{Redis}

\smallskip
\cvsubsection{Other: }
\cvtag{Apache Kafka}
\cvtag{Docker}
\cvtag{Kubernetes}
\cvtag{Git}
\cvtag{GNU/Linux}
\cvtag{NixOS}



\cvsection{Languages}

\begin{itemize}
  \item \textbf{Serbian (native)}
  \item \textbf{English (fluent)}
\end{itemize}



\pagebreak



\cvsection{Selected Personal Projects}

\cvsubsection{Web Development}

\cvproject{Frequency Reservation Website For Serbian Radio Amateurs}{yota.yu1srs.org.rs}{yota-laravel}

\begin{itemize}
\item Website I made for Serbian section of international youth amateur radio organization ``Youngsters On The Air'' (\href{https://www.ham-yota.com/}{www.ham-yota.com}).
\item It's made using Laravel, Vue.js, MariaDB and Bootstrap.
\end{itemize}

\divider{}

\cvsubsection{GNU/Linux Administration}

\cvproject{Mail Server}{}{}

\begin{itemize}
\item I host my very own mail server that serves my domain. It runs OpenSMTPD, Dovecot and Rspamd.
\item Hosted on an unmanaged Virtual Private Server with full root and VNC access, where I configured everything from ground up.
\end{itemize}



\cvsection{Education}

\cvevent{B.A.Sc in Computer Engineering}{School of Electrical and Computer Engineering of Applied Studies}{2019 --- 2022}{Belgrade, Serbia}

\divider{}

\cvevent{Computer Electrotechnician}{Electrical Engineering High School ``Nikola Tesla''}{2015 --- 2019}{Belgrade, Serbia}



\cvsection{Interests}

\cvtag{Purely functional programming}
\cvtag{Distributed systems}
\cvtag{Free (as in freedom) software}
\cvtag{Minimalist software}
\cvtag{Unix-like operating systems}

\end{document}
